The path that we have chosen to take begins with an \textit{abstract} problem into which the
\textit{concrete} continuous problems (equations), for which we shall design preconditioners later, 
can be recast. To present the problem, let us first fix the notation.

\subsection{Notation and preliminaries}
Let $V$ be a Hilbert space over some bounded domain $\Omega$. The space of bounded
linear functionals over $V$\footnote{Functional over $V$ is a mapping taking functions 
from $V$ and returning numbers, e.g. $v \mapsto \int_{\Omega} v(x)\,\mathrm{d}x$} 
shall be denoted $\dual{V}$. For $f\in\dual{V}$ the value of the functional in function 
$v\in V$ is $\brack{f, v}_{\dual{V}, V}$. We denote by $(\cdot, \cdot)_V$
the inner product of $V$ and $\norm{\cdot}_V$ shall be the corresponding norm,
i.e. $\norm{u}_V=\sqrt{(u, u)_V}$ for all $u\in V$. The norm of $\dual{V}$ is then 
$\norm{f}_{\dual{V}}=\sup_{v\in V}\tfrac{\semi{\brack{f, v}_{\dual{V},
V}}}{\norm{v}_V}$. Finally, we will use a shorthad notations for the norms and
inner products of $L^2(\Omega)$ and $H^1(\Omega)$ spaces
%
\[
  (u, v) = \int_{\Omega} u(x) v(x)\,\mathrm{d}x,
  \quad
  \norm{u} = \sqrt{(u, u)}
  \quad
  \mbox{ and }
  \quad
  \norm{u}_1 = \sqrt{\norm{u}^2 + \norm{\nabla{u}}^2}.
\]
%

Given $V$ with inner product $(\cdot, \cdot)_V$ suppose that $u\in V$ is fixed and
consider a mapping $f_u: v\rightarrow (u, v)_V$. Using Cauchy-Schwarz theorem\footnote{
  Recall that the angle $\theta$ of two vectors $\la{u}, \la{v} \in \reals^n$ is 
  defined as $\cos{\theta}=\frac{
    \semi{\la{u}\cdot {v}}
  }
  {
    \semi{\la{u}\cdot\la{u}}\semi{\la{v}\cdot\la{v}}
  }$. But then clearly
\[
  \semi{\la{u}\cdot\la{v}} 
  \leq \norm{\la{u}}\norm{\la{v}}
  \quad\quad
  \norm{\la{u}}=\sqrt{\la{u}\cdot\la{u}}
\]
holds for all vectors in $\reals^n$. Cauchy-Schwarz inequality is a generalization
of the statement above.}
%
see e.g. \site{brenner}, we have $\semi{(u, v)_V}\leq\norm{u}_V\norm{v}_V$ and so
$f_u\in \dual{V}$. Looking at $f_u$ we see that (some) elements of $\dual{V}$ can 
be manufactured via inner products. The \textit{Riesz map} theorem states that
\textit{all} the elements can be manufactured this way.

\begin{theorem}[Riesz]\label{thm:riesz}
  Given Hilbert space $V$ with an inner product $(\cdot, \cdot)_V$ there exists
  for every $f\in \dual{V}$ a unique function $\tau f\in V$ such that $\brack{f,
  v}_{\dual{V}, V}=(\tau f, v)_V$ for all $v\in V$. 
  Moreover, $\norm{f}_{dual{V}}=\norm{\tau f}_V$ (the Riesz map $\tau$ is an
  isometry).
\end{theorem}
\begin{proof}
See ?
\end{proof}

Note that in Theorem \ref{thm:riesz} we can consider the space $V$ with a different 
inner product and the choice will give rise to a different Riesz map. This is
illustrated in the next example, which is taken from \site{malek}. 

\begin{example}[Riesz maps for $H^1$]\label{ex:riesz}
  The space $V=H^1_0(\Omega)\subset H^1(\Omega)$ of $H^1$ functions taking zero values 
  on the boundary $\Omega$ is first considered with the inner product inducing the
  $\norm{\cdot}_1$ norm. For $f\in \dual{V}$ given, the definition of
  the Riesz map $\tau$ and the inner product then yields
  % 
  \[
    \brack{f, v}_{\dual{V}, V} = (\tau f, v)_V = (u, v) + (\nabla u, \nabla v)
    \quad \forall v\in V.
  \]
  %
  That is, the Riesz map with respect to this inner product produces $u=\tau f$
  where $u$ is the weak solution of the Helmholtz problem
  \[
    \begin{aligned}
      -\Delta u + u &= f\quad\mbox{ in }\Omega,\\
                  u &= 0\quad\mbox{ on }\partial\Omega.\\
    \end{aligned}
  \]

  We recall now that Poincar{\'e} inequality holds on $V$, i.e. there exists
  constant $C>0$ such that $\norm{u} \leq C \norm{\nabla u}$ for all $u\in V$. In
  turn $\norm{u}^2_1\leq(C^2+1)\norm{\nabla u}^2$ so that
  %
  \[
    (C^2+1)^{-1}\norm{\nabla}^2_1 \leq \norm{\nabla u}^2 \leq
    \norm{u}^2_1\quad\forall u \in V
  \]
  %
  and $u\mapsto \norm{\nabla u}$ thus defines a equivalent norm on $V$. If we next
  define a Riesz map with respect to the inner product inducing the new norm we
  obtain
  %
  \[
    \brack{f, v}_{\dual{V}, V} = (\nabla \tau f, \nabla v) \quad\forall v\in V.
  \]
  %
  The Riesz representation $u=\tau f$of $f$ is therefore a solution of the Poisson 
  problem
  \[
    \begin{aligned}
      -\Delta u &= f\quad\mbox{ in }\Omega,\\
                  u &= 0\quad\mbox{ on }\partial\Omega.\\
    \end{aligned}
  \]
\end{example}
  At this point we are ready to define an abstract problem and discuss its
  well-posedness.

%

\subsection{Existence}
  The abstract continuous problem shall be defined in terms of the bilinear form
  $a:V\times V\rightarrow \reals$ which is assumed to satisfy the following
  assumptions
  %
  \begin{subequations}\label{eq:lm_assume}
  \begin{align}
    \label{eq:contin}
    \mbox{There exists } C > 0 \mbox{ such that } \semi{a(u, v)\leq &C\norm{u}_V\norm{v}_V}
    \quad\forall u, v\in V, \\
    %%%%%
    \label{eq:coerc}
    \mbox{There exists }\alpha > 0 \mbox{ such that } \semi{a(u, u)\geq &\alpha\norm{u}^2_V}
    \quad\forall u\in V.
  \end{align}
  \end{subequations}
  %
  If \eqref{eq:lm_assume} hold we say that the bilinear form is continous and
  $V$-elliptic.

  Let now $u\in V$ be fixed and define $Au$ by $\brack{Au, v}_{\dual{V}, V}=a(u, v)$. 
  From the continuity condition \eqref{eq:contin} it follows that
  $Au\in\dual{V}$. However, we are interested in a more intriguing problem: given
  $b\in V$ we want to find $u\in V$ such that
  %
  \begin{equation}\label{eq:abstract}
    Au = b\quad\mbox{ in }\dual{V}
    \mbox{ or equivalently}
    \brack{Au, v}_{\dual{V}, V} = \brack{b, v}_{\dual{V}, V}\quad\forall v\in V.
  \end{equation}
  %
  % TODO: remark on special case of a symmetric
  Existence of solution of \eqref{eq:abstract} is the subject of Lax-Milgram
  theorem. In a special case when the bilinear form $a$ is symmetric\footnote{As a
  consequence we have 
  $\brack{Au, v}_{\dual{V}, V}=a(u, v)=a(v, u) = \brack{Av, u}_{\dual{V}, V}$} the
  existence follows from Theorem \ref{thm:riesz}. More specifically, if
  \eqref{eq:lm_assume} hold then due to symmetry of $a$ the bilinear form induces
  an inner product on $V$ and the representation theorem gives $u$ as $\tau b$
  where $\tau$ is the Riesz map with respect to the induced inner product. Note
  that in this case $\norm{u}_{V}=\norm{\tau}_{\dual{V}}$.

  % TODO: theorem+proof
  \begin{theorem}[Lax-Milgram]\label{thm:lm} Assume that \eqref{eq:lm_assume} hold.
  For any $b\in\dual{V}$ there exists a unique solution $u\in V$ of \eqref{eq:abstract}.
    Moreover $\norm{u}_V\leq \tfrac{1}{\alpha}\norm{b}_{\dual{V}}$.
  \end{theorem}
  \begin{proof}
  The following constructive proof can be found in \site{brenner}. We reproduce it here
  as it will be our first encounter with iterative algorithm (for solving \eqref{eq:abstract}).

  Let $u_0\in V$ be some guess for solution of \eqref{eq:abstract}. Since $b-Au=0$ for the
  exact solution it seems reasonable to build a procedure for improving the guess 
  using the residual $b-Au_0$. However, as the two are in different space, 
  $u_0\in V$ while $b-Au_0\in \dual{V}$, they cannot simply be added together. To
  transform the residual to the solution space a mapping the dual space is needed. 
  But we have already seen such a transformation! Using the Riesz map $\tau$ (Theorem
  \ref{thm:riesz} let us now define the iterative procedure for solving
  \eqref{eq:abstract}
  %
    \begin{equation}\label{eq:richardson}
      u_0 \leftarrow u_0 + \rho \tau (b-Au_0) =: T u_0
    \end{equation}
  %
  with $\rho$ a constant parameter to be suitably adjusted.
  
  Since $V$ is also a Banach space the proof that \eqref{eq:richardson}
  converges to a limit (solution) $u\in V$ uses Banach fixed point theorem. Thus
  contraction property of the mapping $T$ is needed: there exists $\epsilon < 1$
  such that
  %
  \[
    \norm{T(u_1 - u_2)}_V \leq \epsilon \norm{u_1 - u_2}_V \quad \forall u_1, u_2\in V.
  \]
  %
  This, however, follows from \eqref{eq:lm_assume} and properties of the Riesz
  map. Indeed letting $v=u_1-u_2$ we have
  %
    \[
  \begin{split}
    \norm{Tv}^2_V &= \norm{v-\rho\tau A v}^2_V = (v-\rho\tau A v, v-\rho\tau A v)_V\\
                &=\norm{v}^2_V - 2\rho(\tau A v, v)_V + \rho^2(\tau A v, \tau A v)_V\\
                &=\norm{v}^2_V - 2\rho\brack{A v, v}_V + \rho^2(\tau A v, \tau Av)_V
                \mathrlap{\textcolor{gray}{\text{ by} \brack{Au, v}_{\dual{V}, V}=a(u, v)}}\\
                &\leq \norm{v}^2_V - 2\rho\alpha\norm{v}^2_V + \rho^2(\tau A v, \tau Av)_V
                \mathrlap{\textcolor{gray}{\text{ by \eqref{eq:coerc}}}}\\
                &\leq \norm{v}^2_V - 2\rho\alpha\norm{v}^2_V + \rho^2\brack{A v, \tau Av)_{\dual{V}, V}}
                \mathrlap{\textcolor{gray}{\text{ by Riesz}}}\\
                &\leq \norm{v}^2_V - 2\rho\alpha\norm{v}^2_V + \rho^2 a(v, \tau Av)
                \mathrlap{\textcolor{gray}{\text{ by definition of } A}}\\
                &\leq \norm{v}^2_V - 2\rho\alpha\norm{v}^2_V + \rho^2 C
                \norm{v}_V\norm{\tau Av}_V
                \mathrlap{\textcolor{gray}{\text{ by \eqref{eq:contin}}}}\\
                &= \norm{v}^2_V - 2\rho\alpha\norm{v}^2_V + \rho^2 C \norm{v}_V\norm{Av}_V
                \mathrlap{\textcolor{gray}{\text{ by Riesz isometry }}}\\
                &\leq (1 - 2\rho\alpha + \rho^2 C^2)\norm{v}^2_V
                \mathrlap{\textcolor{gray}{\text{ by \eqref{eq:contin}}}}.\\
  \end{split}
    \]
  %
  To ensure that $(1 - 2\rho\alpha + \rho^2 C^2) < 1$ it now suffices to chose
  $\rho$ from the interval $(0, \tfrac{2\alpha}{C^2})$. Note that the smallest
  $\epsilon=1-\tfrac{\alpha^2}{C^2}$ is obtained for $C=\tfrac{\alpha}{C^2}$. Since
  the mapping $T$ is a contraction there exists a unique fixed point, $u=Tu$.

  Finally, the estimate of $u$ in terms of the right-hand side follows 
    from ellipticity of $a$ and the fact that $u$ solves \eqref{eq:abstract}
  \[
    \alpha\norm{u}^2_V \leq a(u, u) = \brack{A u, u}_{\dual{V}, V} = 
    \brack{f, u}_{\dual{V}, V} \leq \norm{f}_{\dual{V}}\norm{u}_V.
  \]
  \end{proof}
  
  % TODO: cond of operator
  %Following Lax-Milgram theorem we know that problem \eqref{eq:abstract} has
  %a unique solution and we can address convergence rate of the algorithm proposed
  %in the proof. Letting $u_k\in V$ denote the $k$-th vector computed by the
  %procedure we recall that the iterates are computed as $u_k = T u_{k-1}$ and the
  %solution $u$ of \eqref{eq:absract} satifies $u=Tu$. Letting now $e_k=u - u_k\in V$
  %be the error of $k$-th vector we observe that $e_k = T e_{k-1}$. Thus
  %$\norm{e_{k+1}}_V = \norm{T e_{k}} \leq \epsilon \norm{e_k}_V$ where $\epsilon$
  %is the contraction constant from the proof.
  %generated by algorithm \eqref{eq:richardson} and the error in the solution of
  %\eqref{eq:abstract} we see, cf. proof of Lax-Milgram theorem, that the norm of the 
  %error is governed by $\norm{Te_k}_V$
  

  % TODO: discretization
